\documentclass[12pt]{article}
\title{Example Quiz}
\begin{document}
\begin{abstract}
For the purposes of demonstrating proposed technology \\
\textbf{2} toss-ups, \textbf{2} bonus sets.  Skip bonuses.  \textbf{10} points per toss-up.  \textbf{10} points per bonus.  \textbf{3} boni per set.  Powers are worth \textbf{15}.\\
\end{abstract}
\maketitle
\textbf{1}.
\textit{Instructions: Read the words from left to right. }\\
 Why did the chicken cross the road? \\
, To get to the other side. \\, To avoid his ex. \\
\textit{Instructions: Accept either, or clear knowledge equivalents. }\\
\textbf{2}. \textbf{70} points.
 Who was the President  with the surname Adams  who was not John Q. Adams? \\
, John Adams \\
\textit{Instructions: Do NOT acept John Q. Adams at any point. }\\
Bonus sets.
\textbf{1}.
A town is full of buildings.  Some tall, some short, some wide and some narrow.
\textbf{1}.
 Who was the girl? \\
, Mary \\
\textbf{2}.
 Who was the dog? \\
, Mungo \\
\textbf{3}.
 Who was the mouse? \\
, Midge \\
\textbf{2}.
20 points per bonus.
\textit{Instructions: Do not mispronounce words }\\
Sometimes you need examples.  Here are some examples of examples.
\textbf{1}. 20 points.
 What is the first one? \\
, Foo \\
\textit{Instructions: "Foo" is pronounced "phu". }\\
\textbf{2}.
 What is the second one? \\
, Bar \\
\textbf{3}. 20 points.
 What is the third one? \\
, Baz \\
\textbf{4}. 20 points.
\textit{Instructions: Note to Americans: this does not mean "quarter" }\\
 What is the fourth one? \\
, Quux \\
\textit{Instructions: Accept any feasible pronunciation }\\
\end{document}

