\documentclass[12pt]{article}
\usepackage{titlesec}
\titlespacing*{\subsubsection}{0pt}{0ex}{1.5ex plus .2ex}
\titleformat{\subsection}[runin]{}{}{}{}[]
\titleformat{\subsubsection}[runin]{}{}{}{}[]
\title{Example Quiz}
\begin{document}
\begin{abstract}
For the demonstration proposed XML-powered quizzing, and for related purposes. \\
\textbf{2} toss-ups, \textbf{2} bonus sets.  Skip bonuses.  \textbf{10} points per toss-up.  \textbf{10} points per bonus.  \textbf{3} boni per set.  Powers are worth \textbf{15}.\\
\end{abstract}
\maketitle
\section*{Toss-ups}

\subsection*{\textbf{1.}}
\textit{(Note: Read the words from left to right.)}  Why did the chicken cross the road? \\
ANSWER: 
\textbf{To get to the other side}, \textbf{To avoid his ex}.
\textit{(Note: Accept either, or clear knowledge equivalents.)}
\subsection*{\textbf{2.}} \textit{This toss-up is worth \textbf{70} points.}\\  Who was the President  with the surname Adams  who was not John Q. Adams? \\
ANSWER: 
\textbf{John Adams}.
\textit{(Note: Do NOT acept John Q. Adams at any point.)}
\section*{Bonus sets}

\subsection*{\textbf{1.}}
A town is full of buildings.  Some tall, some short, some wide and some narrow.
\subsubsection*{\textbf{i.}}
Who was the girl?\\
ANSWER: 
\textbf{Mary}.
\subsubsection*{\textbf{ii.}}
Who was the dog?\\
ANSWER: 
\textbf{Mungo}.
\subsubsection*{\textbf{iii.}}
Who was the mouse?\\
ANSWER: 
\textbf{Midge}.
\subsection*{\textbf{2.}}
\textit{These boni are worth \textbf{20} points each.}
\textit{(Note: Do not mispronounce words)}
Sometimes you need examples.  Here are some examples of examples.
\subsubsection*{\textbf{i.}} \textit{This bonus is worth \textbf{15} points.}
What is the first one?\\
ANSWER: 
\textbf{Foo}.
\textit{(Note: "Foo" is pronounced "phu".)}
\subsubsection*{\textbf{ii.}}
What is the second one?\\
ANSWER: 
\textbf{Bar}.
\subsubsection*{\textbf{iii.}} \textit{This bonus is worth \textbf{25} points.}
What is the third one?\\
ANSWER: 
\textbf{Baz}.
\subsubsection*{\textbf{iv.}} \textit{This bonus is worth \textbf{30} points.}
\textit{(Note: Note to Americans: this does not mean "quarter")}
What is the fourth one?\\
ANSWER: 
\textbf{Quux}.
\textit{(Note: Accept any feasible pronunciation)}
\end{document}

